\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-01-26 doc/chapters/usage.tex
add illustration of the workflow

Creating a spectrum generator with \flexisusy consists of the
following steps:
%
\begin{enumerate}
\item Creating a \emph{SARAH model file}.  Note, that SARAH already
  ships a lot of pre-defined model files in \code{SARAH/Models/} that
  can be used.
\item Creating a \emph{\flexisusy model file} in
  \code{models/<model-name>/}.  The \code{createmodel} script will
  help you creating one, see Section~\ref{sec:createmodel}.  For more
  details on how to write a \flexisusy model file see
  Section~\ref{sec:model-files}.
\item \emph{Configure} \flexisusy with your desired model, see
  Section~\ref{sec:configure}.
\item Run \code{make}.  This will create the C++ code for your
  spectrum generator and compile it, see Section~\ref{sec:make}.
\end{enumerate}

>>>>

Creating a spectrum generator with \flexisusy consists of the
following steps:
%
\begin{enumerate}
  \setcounter{enumi}{-1}
\item Creating a \emph{SARAH model file}.  The SARAH model file must
  be loadable via \code{Start["<model-name>"]}.  Note, that SARAH
  already ships a lot of pre-defined model files in
  \code{SARAH/Models/} that can be used.
\item Creating a \emph{\flexisusy model file} in
  \code{models/<model-name>/}.  The \code{createmodel} script will
  help you creating one, see Section~\ref{sec:createmodel}.  For more
  details on how to write a \flexisusy model file see
  Section~\ref{sec:model-files}.
\item \emph{Configure} \flexisusy with your desired model, see
  Section~\ref{sec:configure}.
\item Run \code{make}.  This will create the C++ code for your
  spectrum generator and compile it, see Section~\ref{sec:make}.
\end{enumerate}
%
The steps 1--3 are illustrated in \figref{fig:workflow}.

\begin{figure}[tbh]
  \centering
  \begin{tikzpicture}[node distance = 3.5cm, auto]
    \node[block, text width=14em] (createmodel) {%
      \code{./createmodel --name=NMSSM}};
    \node[block, text width=14em, below of=createmodel] (configure) {%
      \code{./configure --with-models=NMSSM}};
    \node[block, text width=14em, below of=configure] (make) {%
      \code{make}};
    \node[cloud, text width=22em, right=1.6cm of createmodel] (createmodel-output) {%
      Creates the files:\\%
      \code{./models/NMSSM/module.mk}\\%
      \code{./models/NMSSM/start.m}\\%
      \code{./models/NMSSM/FlexibleSUSY.m}};
    \node[cloud, text width=22em, right=1.6cm of configure] (configure-output) {%
      Creates \code{./Makefile} which includes\\%
      \code{./models/NMSSM/module.mk}};
    \node[cloud, text width=22em, right=1.6cm of make] (make-output) {%
      \begin{enumerate}\itemsep0em
      \item Runs the meta code \code{math -run
          "Get[\"./models/NMSSM/start.m\"];"} which creates the C++
        source files.
      \item The source files are then compiled to
        \code{./models/NMSSM/libNMSSM.a} and linked against the
        executable \code{./models/NMSSM/run\_NMSSM.x}.
      \end{enumerate}};
    \path[arrow] (createmodel) -- (configure);
    \path[arrow] (configure) -- (make);
    \path[draw, dashed] (createmodel) -- (createmodel-output);
    \path[draw, dashed] (configure) -- (configure-output);
    \path[draw, dashed] (make) -- (make-output);
  \end{tikzpicture}
  \caption{\flexisusy workflow}
  \label{fig:workflow}
\end{figure}
